|

### 2021-05-26 article/article.Rmd
edits to methods section

We compiled our study sample in three rounds. In the first search round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in
English and, to ensure that studies were comparable, we only included papers
that used quantitative methods to investigate the relationship between
legislature size and public spending\footnote{Please refer to Section C in the
Supplementary Material for a detailed description of the selection procedure.
We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
resulting papers after each review step.}. After this stage, we identified the
variables authors most commonly employ to measure government expenditure and
legislature size, our dependent and independent variables, respectively. For
government expenditure, our study sample uses (i) public expenditure as a share
of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
public expenditure per capita as its main variables of interest\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables.}. In regards to legislature size, the variables are (i) lower
chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
house size\footnote{There are a few important nuances concerning coding of
these variables. For instance, unicameralism is captured both by lower chamber
size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
literature estimates how institutional designs affect this relationship, ours
and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any articles that used the natural
logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. We again restricted the search to articles written in English
which employed quantitative methods. In the third search round, we looked into
the personal webpages of every author we had already included in our previous
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript which we might had missed in the
previous queries. All papers we found in that last search had already been
included in our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

@@

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets, and almost all papers fit more
than one model with similar variables, what suggests that the assumption does
not hold. We use two procedures to tackle this problem. First, we created two
sets of study coefficients to reduce the impact of multicollinearity in our
estimations. The first group includes only the most rigorous models from each
paper, that is, those estimated with the largest $n$, most control variables,
and fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the optimal
bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
two dependent or independent variables of interest\footnote{The papers that
used more than one dependent or independent variable of interest are
\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency. More
information about the multilevel models can be found in Section H of the
Supplementary Material.

>>>>

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in the
English language, and to make our study sample comparable, we only selected
papers that use quantitative methods to analyse data\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables. Please refer to Section C in the Supplementary Material for a
detailed description of the selection procedure. We also included two PRISMA
(Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow
diagrammes \citep{liberati2009prisma} showing the number of resulting papers
after each review step.}. After this stage, we identified the variables that
authors employ more often to measure government expenditure and legislature
size, our dependent and independent variables, respectively. For government
expenditure, our study sample uses (i) public expenditure as a share of GDP;
(ii) public expenditure per capita; and (iii) the natural logarithm of public
expenditure per capita as its main variables of interest. In regards to
legislature size, the variables are (i) lower chamber size; (ii) natural
logarithm of lower chamber size; and (iii) upper house size\footnote{There are
a few important nuances concerning coding of these variables. For instance,
unicameralism is captured both by lower chamber size ($n = 7$) and by log lower
chamber size ($n = 5$). Since much of the literature estimates how
institutional designs affect this relationship, ours and many other articles
use both lower and upper chamber sizes as main explanatory variables. We did
not find any articles that used the natural logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. In the third
search round, we looked into the personal webpages of every author we had
already included in our previous sample. The purpose of this manual search was
to assess whether there was any working paper or unpublished manuscript which
we might had missed in the previous queries. All papers we found in the last
search had already been included in our sample. Combined, the three searches
produced a dataset of `r length(unique(dat$id))` studies as of the
10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
list of articles we analyse in this paper.

@@

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets in their analyses,
and almost all papers fit more than one model with similar variables, what
suggests that the assumption does not hold. We use two procedures to tackle this
problem. First, we created two sets of study coefficients to reduce the impact
of multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
articles analysed two dependent or independent variables of
interest\footnote{The papers that used more than one dependent or independent
variable of interest are \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are very similar when we use the extended
set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency and improving
the accuracy of the results. More information about the multilevel models can
be found in Section H of the Supplementary Material.
